Geometrization of characters of tori over non-Archimedean local fields

### 2013-07-22 shanghai.tex
Added remark about actions on sheaves, and some paragraphs on the CS version of the norm map.

@@

When using character sheaves to study characters, it is useful to understand
how character sheaves behave under change of fields.
Suppose that $k'$ is a finite extension of $k$, $G$ is an abelian group scheme
over $k$ as in Theorem \ref{thm:snake} and $G_{k'}$ is the base change of $G$ to $k'$.
We define a functor $\CS(G_{k'}) \to \CS(G)$ by.... \David{We can't define this by pullback
since $G_{k'} \to G$ goes in the wrong direction}
\begin{proposition} \label{prop:csbe}
The diagram
\[
\begin{tikzcd}
\CSiso{G_{k'}} \arrow[two heads]{r} \dar & \CSiso{G} \dar \\
\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx)
\end{tikzcd}
\]
commutes, where the vertical arrows are as in Theorem \ref{thm:snake}.
\end{proposition}

>>>>

\begin{remark} \label{rem:CS-action}
If $W$ is a group equipped with a homomorphism $\alpha : W \to \Gal(\bFq/\Fq)$
then an \emph{action} of $W$ on $\gcs{L}$ is a collection of isomorphisms
\[
\gamma_w : \alpha(w)^* \gcs{L} \to \gcs{L}
\]
so that $\gamma_{uw} = \gamma_w \circ \alpha(w)^*\gamma_u$. \David{make sure I have the order right and add a reference}
Specifying an $F$ as in \ref{CS.2} is the same as giving an action of the Weil group $W_k$
on $\gcs{L}$ compatible with $\mu$.
\end{remark}

@@

When using character sheaves to study characters, it is useful to understand
how character sheaves behave under change of fields.
Suppose that $k'$ is a finite extension of $k$ of degree $n$, $G$ is an abelian group scheme
over $k$ as in Theorem \ref{thm:snake} and $G_{k'}$ is the base change of $G$ to $k'$.
If $\cs{L} = (\gcs{L}, \mu, F)$ is a character sheaf on $G$ we may define
a character sheaf $\cs{L}_{k'} = (\gcs{L}, \mu, F_{k'})$ on $G_{k'}$ by setting
\[
F_{k'} = F \circ \Frob_G^*(F) \circ \cdots \circ (\Frob_G^{n-1})^*(F).
\]
The commutativity of the diagram (CS.2) for $F_{k'}$ follows from the fact that $\Frob_{G_{k'}} = \Frob_G^n$.

\begin{proposition}
The diagram
\[
\begin{tikzcd}
\CSiso{G} \rar \dar & \CSiso{G_{k'}} \dar \\
\Hom(G(k), \EEx) \rar & \Hom(G(k'), \EEx)
\end{tikzcd}
\]
commutes, where vertical arrows are as in Theorem \ref{thm:snake}, the top arrow is as above,
and the bottom is induced by the norm map $G(k') \to G(k)$.
\end{proposition}

We define a functor $\CS(G_{k'}) \to \CS(G)$ by.... \David{We can't define this by pullback
since $G_{k'} \to G$ goes in the wrong direction}
\begin{proposition} \label{prop:csbe}
The diagram
\[
\begin{tikzcd}
\CSiso{G_{k'}} \arrow[two heads]{r} \dar & \CSiso{G} \dar \\
\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx)
\end{tikzcd}
\]
commutes, where the vertical arrows are as in Theorem \ref{thm:snake}.
\end{proposition}
